The ChEMBL database as Linked Open Data

### 2013-03-06 article.tex
Explained why custom scripts are used, and how the data is practically converted
Added a note about automated validation

The ChEMBL version used in this paper is ChEMBL 13, which was released on 29 February 2012.
The SQL data dump provided by ChEMBL was inserted into a local MySQL database. A set of SQL queries 
were then executed to generate RDF triples using a set of PHP scripts. These scripts are Open Source 
and are available from the source code hosting service, GitHub~\cite{ChEMBLRDFGitHub}. This process 
has been outlined in a best practices note by the W3C Health Care and Life Sciences Interest
Group~\cite{Marshall2012}. This process has not changed much since its original description.

@@

Reproduction of the ChEMBL release statistics through querying ChEMBL-RDF with SPARQL 
provides end users with a high degree of confidence that the ChEMBL-RDF contains the same 
core content as the source relational database.

>>>>

The ChEMBL version used in this paper is ChEMBL 13, which was released on 29 February 2012.
The SQL data dump provided by ChEMBL was inserted into a local MySQL database. A set of SQL queries 
were then executed to generate RDF triples using a set of PHP scripts. The scripts use SQL to
query the database and output triples using print statements. Custom PHP scripts have been used
as a light-weight soluton to provide a Linked Data API via a Apache webserver, as well as to
create data files with triples. These scripts are Open Source 
and are available from the source code hosting service, GitHub~\cite{ChEMBLRDFGitHub}. This process 
has been outlined in a best practices note by the W3C Health Care and Life Sciences Interest
Group~\cite{Marshall2012}. This process has not changed much since its original description.

@@

Reproduction of the ChEMBL release statistics through querying ChEMBL-RDF with SPARQL 
provides end users with a high degree of confidence that the ChEMBL-RDF contains the same 
core content as the source relational database. The development of a validation test suite
is being discussed but not yet implemented; testing criteria other then the here presented
summarizing counts would change with each release due to curation events. Interactive,
manual curation of the conversion process as employed by the authors already is more effective
at this moment.
